Formalization of Typed Lua

### 2015-06-12 doc/papers/paper/paper.tex
DLS paper: change shape to point

In this paper, we give a formal basis to an updated version of that design, with a focus on novel type system features
that Typed Lua uses to type some tricky Lua idioms.
One of these idioms is the use of assignment to
build records and objects one field at a time, as in
the following example, where the {\tt newshape} function
is a constructor for objects with {\tt x} and {\tt y}
fields and a {\tt move} method:
\begin{verbatim}
  function new_shape(x, y)
    local shape = {}
    shape.x = x
    shape.y = y
    function shape:move(dx, dy)
      self.x = self.x + dx
      self.y = self.y + dy
      return self
    end
    return shape
  end
\end{verbatim}

>>>>

In this paper, we give a formal basis to an updated version of that design, with a focus on novel type system features
that Typed Lua uses to type some tricky Lua idioms.
One of these idioms is the use of assignment to
build records and objects one field at a time, as in
the following example, where the {\tt newpoint} function
is a constructor for objects with {\tt x} and {\tt y}
fields and a {\tt move} method:
\begin{verbatim}
  function new_point(x, y)
    local point = {}
    point.x = x
    point.y = y
    function point:move(dx, dy)
      self.x = self.x + dx
      self.y = self.y + dy
      return self
    end
    return point
  end
\end{verbatim}
